Model LF

### 2022-12-07 Power point test.Rmd
Commit

```{r, echo=FALSE}
wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr
wage_gap1_00 = S_model$simulation$wage_gap1
wage_ds_t_00 = S_model$simulation$wage_ds_t
u_ds_00 = S_model$simulation$u_ds

kuld_00 = S_model$simulation$kuld

shock_kuld_00 = S_model$simulation$shock_kuld
kont_h_ratio_00 = S_model$simulation$kont_h_ratio

yk_ds_00 = S_model$simulation$yk_ds
part_00 = S_model$simulation$part
lf_00 = S_model$simulation$lf
pconk_ds_00 = S_model$simulation$pconk_ds
yd_h1_00 = S_model$simulation$yd_h1 
nben_h_rest_00 = S_model$simulation$nben_h_rest
nben_h_un_00 = S_model$simulation$nben_h_un
komp_r_00 = S_model$simulation$komp_r
nben_h_00 = S_model$simulation$nben_h
wageindex_00 = S_model$simulation$wageindex
yh1_00 = S_model$simulation$yh1
yd1_h_00 = S_model$simulation$yd1_h
yd_hk_00 = S_model$simulation$yd_hk
yd_h_00 = S_model$simulation$yd_h
l_h_tr_00 = S_model$simulation$l_h_tr
s_h_00 = S_model$simulation$s_h
eq_h_00 = S_model$simulation$eq_h
iba_h_00 = S_model$simulation$iba_h
yd1_hk_ds_00 = S_model$simulation$yd1_hk_ds
ur_00 = S_model$simulation$ur
ur_ds_00 = S_model$simulation$ur_ds
iba_f_tr_00 = S_model$simulation$iba_f_tr
iba_h_tr_00 = S_model$simulation$iba_h_tr
iba_nf_tr_00 = S_model$simulation$iba_nf_tr
nl_nf_00 = S_model$simulation$nl_nf
neq_nf_tr_00 = S_model$simulation$neq_nf_tr
l_nf_tr_00 = S_model$simulation$l_nf_tr
sec_nf_tr_00 = S_model$simulation$sec_nf_tr
ins_nf_tr_00 = S_model$simulation$ins_nf_tr
neq_nf_00 = S_model$simulation$neq_nf
i_nf_00 = S_model$simulation$i_nf
np_nf_00 = S_model$simulation$np_nf
s_nf_00 = S_model$simulation$s_nf
yh_nf_00 = S_model$simulation$yh_nf
y_00 = S_model$simulation$y
b2_nf_r_00 = S_model$simulation$b2_nf_r
p_tax_00 = S_model$simulation$p_tax
b2_00 = S_model$simulation$b2
w_nf_00 = S_model$simulation$w_nf
npropinc_nf_00 = S_model$simulation$npropinc_nf
int_nf_00 = S_model$simulation$int_nf
div_nf_00 = S_model$simulation$div_nf
eq_nf_a_f_00 = S_model$simulation$eq_nf_a_f
eq_nf_l_nf_00 = S_model$simulation$eq_nf_l_nf
eq_nf_a_nf_00 = S_model$simulation$eq_nf_a_nf
eq_h_nf_00 = S_model$simulation$eq_h_nf
eq_row_a_nf_00 = S_model$simulation$eq_row_a_nf
eq_f_a_nf_00 = S_model$simulation$eq_f_a_nf
eq_g_nf_00 = S_model$simulation$eq_g_nf
eq_nf_a_row_00 = S_model$simulation$eq_nf_a_row
neq_nf_00 = S_model$simulation$neq_nf
check_div_00 = S_model$simulation$check_div
xk_ds_00 = S_model$simulation$xk_ds
g_00 = S_model$simulation$g
rw_ds_00 = S_model$simulation$rw_ds
b2_00 = S_model$simulation$b2
test = S_model$simulation$test

### Gengivelse
yk_ds_00 = S_model$simulation$yk_ds
emp_00 = S_model$simulation$emp
wage_ds_00 = S_model$simulation$wage_ds
unemp_00 = S_model$simulation$unemp
ik_00 = S_model$simulation$ik
pc_ds_00 = S_model$simulation$pc_ds
yd_hk_ds_00 = S_model$simulation$yd_hk_ds

### Test

yd1_hk_ds_00 = S_model$simulation$yd1_hk_ds
yd2a_hk_ds_00 = S_model$simulation$yd2a_hk_ds
yd2b_hk_00 = S_model$simulation$yd2b_hk
yd1_hk_00 = S_model$simulation$yd1_hk
yd2a_hk_00 = S_model$simulation$yd2a_hk
yd1_h_00 = S_model$simulation$yd1_h
yh1_00 = S_model$simulation$yh1
sec_g_tr_00 = S_model$simulation$sec_g_tr
sec_f_d_tr_g_00 = S_model$simulation$sec_f_d_tr_g
sec_h_tr_g_00 = S_model$simulation$sec_h_tr_g
l_h_00 = S_model$simulation$l_h
yd2b_h_00 = S_model$simulation$yd2b_h
yh2b_00 = S_model$simulation$yh2b
propinc_p_h_00 = S_model$simulation$propinc_p_h
int_p_h_00 = S_model$simulation$int_p_h
iloan_00 = S_model$simulation$iloan
int_p_h_adj_00 = S_model$simulation$int_p_h_adj

## RESCHECK
yk_00 = S_model$simulation$yk
prodk_00 = S_model$simulation$prodk
pcon_00 = S_model$simulation$pcon
i_00 = S_model$simulation$i
x_00 = S_model$simulation$x
m_00 = S_model$simulation$m
i_h_00 = S_model$simulation$i_h
w_nf_00 = S_model$simulation$w_nf
s_nf_00 = S_model$simulation$s_nf
pconk_00 = S_model$simulation$pconk
ik_00 = S_model$simulation$ik
gk_00 = S_model$simulation$gk
xk_00 = S_model$simulation$xk
mk_00 = S_model$simulation$mk
g_00 = S_model$simulation$g
ur_00 = S_model$simulation$ur
ur_ds_00 = S_model$simulation$ur_ds
prod_ds_00 = S_model$simulation$prod_ds
int_r_h_00 = S_model$simulation$int_r_h
int_p_h_00 = S_model$simulation$int_p_h
div_h_00 = S_model$simulation$div_h
aa_check_00 = S_model$simulation$aa_check
insu_h_00 = S_model$simulation$insu_h
propinc_r_h_00 = S_model$simulation$propinc_r_h
propinc_p_h_00 = S_model$simulation$propinc_p_h
yh_h_00 = S_model$simulation$yh_h
yh2a_00 = S_model$simulation$yh2a
yh1_00 = S_model$simulation$yh1
w_h_r_00 = S_model$simulation$w_h_r
yd2a_h_00 = S_model$simulation$yd2a_h
yd2b_h_00 = S_model$simulation$yd2b_h 
yd1_h_00 = S_model$simulation$yd1_h
tax_h_00 = S_model$simulation$tax_h
yd1_hk_00 = S_model$simulation$yd1_hk
yd2a_hk_00 = S_model$simulation$yd2a_hk
yd2b_hk_00 = S_model$simulation$yd2b_hk
yd_h_00 = S_model$simulation$yd_h
nsben_h_00 = S_model$simulation$nsben_h
yd_h1_00 = S_model$simulation$yd_h1
nl_h_00 = S_model$simulation$nl_h
pconk_ds_00 = S_model$simulation$pconk_ds
pconk_00 = S_model$simulation$pconk
pcon_00 = S_model$simulation$pcon
i_bd_h_k_00 = S_model$simulation$i_bd_h_k
i_equip_h_k_00 = S_model$simulation$i_equip_h_k
iba_h_00 = S_model$simulation$iba_h
sec_h_00 = S_model$simulation$sec_h
sec_h_tr_g_00 = S_model$simulation$sec_h_tr_g
l_h_00 = S_model$simulation$l_h
eq_h_tr_00 = S_model$simulation$eq_h_tr
iba_h_tr_00 = S_model$simulation$iba_h_tr
eq_h_nf_00 = S_model$simulation$eq_h_nf
eq_h_f_00 = S_model$simulation$eq_h_f
eq_h_row_00 = S_model$simulation$eq_h_row
eq_h_nf_tr_00 = S_model$simulation$eq_h_nf_tr
eq_h_f_tr_00 = S_model$simulation$eq_h_f_tr
eq_h_row_tr_00 = S_model$simulation$eq_h_row_tr
eq_h_test_00 = S_model$simulation$eq_h_test
ins_h_00 = S_model$simulation$ins_h
ins_h_tr_00 = S_model$simulation$ins_h_tr
lev_h_00 = S_model$simulation$lev_h
fa_h_00 = S_model$simulation$fa_h
fnw_h_00 = S_model$simulation$fnw_h
fnw_hk_00 = S_model$simulation$fnw_hk
i_bd_h_00 = S_model$simulation$i_bd_h
i_equip_h_00 = S_model$simulation$i_equip_h
bd_h_k_00 = S_model$simulation$bd_h_k
equip_h_k_00 = S_model$simulation$equip_h_k 
bd_h_00 = S_model$simulation$bd_h
equip_h_00 = S_model$simulation$equip_h
rer_00 = S_model$simulation$rer 
py_00 = S_model$simulation$py
s_00 = S_model$simulation$s
w_nf_00 = S_model$simulation$w_nf
yf_00 = S_model$simulation$yf
ws_00 = S_model$simulation$ws
ps_00 = S_model$simulation$ps 
prate_00 = S_model$simulation$prate 
prate_ds_00 = S_model$simulation$prate_ds 
ps_ds_00 = S_model$simulation$ps_ds
tobinq_00 = S_model$simulation$tobinq
i_bd_nfc_k_00 = S_model$simulation$i_bd_nfc_k
i_equip_nfc_k_00 = S_model$simulation$i_equip_nfc_k
i_h_00 = S_model$simulation$i_h 
i_nf_00 = S_model$simulation$i_nf
i_f_00 = S_model$simulation$i_f 
i_g_00 = S_model$simulation$i_g 
int_nf_00 = S_model$simulation$int_nf
div_nf_00 = S_model$simulation$div_nf
insu_nf_00 = S_model$simulation$insu_nf
npropinc_nf_00 = S_model$simulation$npropinc_nf
yh_nf_00 = S_model$simulation$yh_nf
tax_nf_00 = S_model$simulation$tax_nf
nl_nf_00 = S_model$simulation$nl_nf 
iba_nf_00 = S_model$simulation$iba_nf 
iba_nf_tr_00 = S_model$simulation$iba_nf_tr
sec_nf_00 = S_model$simulation$sec_nf
l_nf_00 = S_model$simulation$l_nf
eq_nf_a_00 = S_model$simulation$eq_nf_a
eq_nf_a_nf_00 = S_model$simulation$eq_nf_a_nf 
eq_nf_l_nf_00 = S_model$simulation$eq_nf_l_nf
eq_nf_ax_00 = S_model$simulation$eq_nf_ax 
eq_nf_a_f_00 = S_model$simulation$eq_nf_a_f 
eq_nf_a_row_00 = S_model$simulation$eq_nf_a_row
eq_nf_l_00 = S_model$simulation$eq_nf_l
eq_nf_lx_00 = S_model$simulation$eq_nf_lx
neq_nf_00 = S_model$simulation$neq_nf
neq_nf_tr_00 = S_model$simulation$neq_nf_tr 
eq_nf_a_test_00 = S_model$simulation$eq_nf_a_test
eq_nf_l_test_00 = S_model$simulation$eq_nf_l_test 
ins_nf_00 = S_model$simulation$ins_nf 
fnw_nf_00 = S_model$simulation$fnw_nf
fnw_nfk_00 = S_model$simulation$fnw_nfk 
i_bd_nfc_00 = S_model$simulation$i_bd_nfc
i_equip_nfc_00 = S_model$simulation$i_equip_nfc 
bd_nfc_k_00 = S_model$simulation$bd_nfc_k 
equip_nfc_k_00 = S_model$simulation$equip_nfc_k 
bd_nfc_00 = S_model$simulation$bd_nfc
equip_nfc_00 = S_model$simulation$equip_nfc 
int_f_00 = S_model$simulation$int_f
div_f_00 = S_model$simulation$div_f
insu_f_00 = S_model$simulation$insu_f
propinc_r_f_00 = S_model$simulation$propinc_r_f
propinc_p_f_00 = S_model$simulation$propinc_p_f
npropinc_f_00 = S_model$simulation$npropinc_f
yh_f_00 = S_model$simulation$yh_f
yd_f_00 = S_model$simulation$yd_f
d8_f_00 = S_model$simulation$d8_f
nben_f_00 = S_model$simulation$nben_f 
s_f_00 = S_model$simulation$s_f
nl_f_00 = S_model$simulation$nl_f 
iba_f_00 = S_model$simulation$iba_f 
eq_f_a_00 = S_model$simulation$eq_f_a 
eq_f_a_nf_00 = S_model$simulation$eq_f_a_nf 
eq_f_a_f_00 = S_model$simulation$eq_f_a_f 
eq_f_l_f_00 = S_model$simulation$eq_f_l_f
eq_f_a_row_00 = S_model$simulation$eq_f_a_row 
eq_f_ax_00 = S_model$simulation$eq_f_ax
eq_f_l_00 = S_model$simulation$eq_f_l
eq_f_lx_00 = S_model$simulation$eq_f_lx 
neq_f_00 = S_model$simulation$neq_f 
neq_f_tr_00 = S_model$simulation$neq_f_tr 
eq_f_l_test_00 = S_model$simulation$eq_f_l_test 
sec_f_d_00 = S_model$simulation$sec_f_d 
sec_f_d_tr_00 = S_model$simulation$sec_f_d_tr 
sec_f_d_tr_nf_00 = S_model$simulation$sec_f_d_tr_nf
sec_f_d_tr_g_00 = S_model$simulation$sec_f_d_tr_g 
sec_f_a_00 = S_model$simulation$sec_f_a 
sec_f_a_tr_00 = S_model$simulation$sec_f_a_tr 
l_f_00 = S_model$simulation$l_f 
l_f_tr_00 = S_model$simulation$l_f_tr 
ins_f_00 = S_model$simulation$ins_f 
ins_f_tr_00 = S_model$simulation$ins_f_tr 
fnw_f_00 = S_model$simulation$fnw_f
fnw_fk_00 = S_model$simulation$fnw_fk 
i_bd_fc_00 = S_model$simulation$i_bd_fc 
i_equip_fc_00 = S_model$simulation$i_equip_fc 
bd_fc_k_00 = S_model$simulation$bd_fc_k 
equip_fc_k_00 = S_model$simulation$equip_fc_k 
bd_fc_00 = S_model$simulation$bd_fc
equip_fc_00 = S_model$simulation$equip_fc
int_g_00 = S_model$simulation$int_g 
div_g_00 = S_model$simulation$div_g 
insu_g_00 = S_model$simulation$insu_g 
propinc_r_g_00 = S_model$simulation$propinc_r_g 
propinc_p_g_00 = S_model$simulation$propinc_p_g 
npropinc_g_00 = S_model$simulation$npropinc_g 
yh_g_00 = S_model$simulation$yh_g 
yd_g_00 = S_model$simulation$yd_g 
nben_g_00 = S_model$simulation$nben_g 
tax_g_00 = S_model$simulation$tax_g 
s_g_00 = S_model$simulation$s_g 
nl_g_00 = S_model$simulation$nl_g 
iba_g_00 = S_model$simulation$iba_g 
eq_g_00 = S_model$simulation$eq_g 
eq_g_nf_00 = S_model$simulation$eq_g_nf
eq_g_f_00 = S_model$simulation$eq_g_f 
eq_g_row_00 = S_model$simulation$eq_g_row 
eq_g_ax_00 = S_model$simulation$eq_g_ax 
eq_g_test_00 = S_model$simulation$eq_g_test 
sec_g_00 = S_model$simulation$sec_g 
sec_g_tr_00 = S_model$simulation$sec_g_tr 
l_g_00 = S_model$simulation$l_g 
ins_g_00 = S_model$simulation$ins_g 
fnw_g_00 = S_model$simulation$fnw_g 
fnw_gk_00 = S_model$simulation$fnw_gk 
i_bd_g_00 = S_model$simulation$i_bd_g 
i_equip_g_00 = S_model$simulation$i_equip_g 
bd_g_k_00 = S_model$simulation$bd_g_k 
equip_g_k_00 = S_model$simulation$equip_g_k 
bd_g_00 = S_model$simulation$bd_g 
equip_g_00 = S_model$simulation$equip_g 
int_row_00 = S_model$simulation$int_row 
div_row_00 = S_model$simulation$div_row 
insu_row_00 = S_model$simulation$insu_row 
propinc_r_row_00 = S_model$simulation$propinc_r_row 
propinc_p_row_00 = S_model$simulation$propinc_p_row 
npropinc_row_00 = S_model$simulation$npropinc_row
s_row_00 = S_model$simulation$s_row
nl_row_00 = S_model$simulation$nl_row
nben_row_00 = S_model$simulation$nben_row 
nx_00 = S_model$simulation$nx 
cab_00 = S_model$simulation$cab 
bop_00 = S_model$simulation$bop 
fab_00 = S_model$simulation$fab 
iba_row_00 = S_model$simulation$iba_row 
iba_row_tr_00 = S_model$simulation$iba_row_tr 
sec_row_00 = S_model$simulation$sec_row 
l_row_00 = S_model$simulation$l_row 
eq_row_a_00 = S_model$simulation$eq_row_a 
eq_row_a_nf_00 = S_model$simulation$eq_row_a_nf 
eq_row_a_f_00 = S_model$simulation$eq_row_a_f
eq_row_ax_00 = S_model$simulation$eq_row_ax 
eq_row_a_test_00 = S_model$simulation$eq_row_a_test 
eq_row_l_00 = S_model$simulation$eq_row_l
eq_row_lx_00 = S_model$simulation$eq_row_lx 
eq_row_l_test_00 = S_model$simulation$eq_row_l_test 
neq_row_00 = S_model$simulation$neq_row
neq_row_tr_00 = S_model$simulation$neq_row_tr 
ins_row_00 = S_model$simulation$ins_row 
fnw_row_00 = S_model$simulation$fnw_row
fnw_rowk_00 = S_model$simulation$fnw_rowk
unadj_00 = S_model$simulation$unadj
unemp_00 = S_model$simulation$unemp 
ur_00 = S_model$simulation$ur 
ur_ds_00 = S_model$simulation$ur_ds
uradj_00 = S_model$simulation$uradj 
lf_00 = S_model$simulation$lf 
pc_00 = S_model$simulation$pc 
mkp_00 = S_model$simulation$mkp
emp_00 = S_model$simulation$emp
urterm_00 = S_model$simulation$urterm 
wage_00 = S_model$simulation$wage 
wageindex_00 = S_model$simulation$wageindex 
wage_ds_00 = S_model$simulation$wage_ds 
prod_00 = S_model$simulation$prod
prod_ds_00 = S_model$simulation$prod_ds 
acc_rate_00 = S_model$simulation$acc_rate 
nl_check_00 = S_model$simulation$nl_check
fnl_check_00 = S_model$simulation$fnl_check
check_np_00 = S_model$simulation$check_np
check_ctr_00 = S_model$simulation$check_ctr 
check_invest_00 = S_model$simulation$check_invest 
check_iba_00 = S_model$simulation$check_iba
check_tax_00 = S_model$simulation$check_tax_00
check_iba_rv_00 = S_model$simulation$check_iba_rv 
check_iba_tr_00 = S_model$simulation$check_iba_tr
check_eq_00 = S_model$simulation$check_eq
check_eq_tr_00 = S_model$simulation$check_eq_tr
check_div_00 = S_model$simulation$check_div
check_l_00 = S_model$simulation$check_l 
check_l_tr_00 = S_model$simulation$check_l_tr
check_ins_00 = S_model$simulation$check_ins
check_ins_tr_00 = S_model$simulation$check_ins_tr
check_sec_00 = S_model$simulation$check_sec
npropinc_h_00 = S_model$simulation$npropinc_h

wage_gap_00 = S_model$simulation$wage_gap
wage_gap_00 = S_model$simulation$shock_kuld

part1_00 = S_model$simulation$part1

mk_ds_00 = S_model$simulation$mk_ds
i_bd_nfc_k_ds_00 = S_model$simulation$i_bd_nfc_k_ds

i_equip_nfc_k_ds_00 = S_model$simulation$i_equip_nfc_k_ds
inflation_00 = S_model$simulation$inflation

net_balance_00= xk_ds_00 - mk_ds_00
```

# Tjek

Plots for paper

```{r, fig.width=12, fig.height=7}
par(mfrow=c(1,2))

plot(yk_ds_00, col= "red", ylab= "GDP" , main= "GDP"); lines(yk_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(emp_00, col= "red", main= "Employment", ylab= "Employment (people)"); lines(emp, col = "blue"); 
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

```{r, fig.width=12, fig.height=7}
par(mfrow=c(1,2))

plot(max_dp_00, col= "red", main= "Maximum level of income insurance", ylab= "Maximum level of income insurance (1000 kr.)"); lines(obs_dp_q, col = "blue"); 
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()

plot(komp_r_00, col= "red", main= "Compensation rate", ylab= "Compensation rate (ratio)"); lines(komp_r_obs1, col = "blue"); 
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()

# Shocks

## Baseline Scenario 1

```{r}
shock_lf_model_shock=shock_lf_model %>% window(start= c(2006,3))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs1 <- list(

 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs1 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs1
                    )
```

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds

xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds

net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1

ik_bs1 = Shock_bs1$simulation$ik
mk_bs1 = Shock_bs1$simulation$mk

ik_ratio_bs1 = ik_bs1/yk_ds_bs1
mk_ratio_bs1 = mk_bs1/yk_ds_bs1

c_ratio_bs1 = pconk_ds_bs1/yk_ds_bs1
```

```{r}
plot(part_bs1, col= "green", main= "Participation rate", ylab= "Participation rate (Ratio)"); lines(part, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

## Baseline Scenario 2

@@

```{r}
plot(wage_ds_t_bs2, col= "green"); lines(wage_ds_t, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

```{r}
plot(wage_gap_bs2, col= "green"); lines(wage_gap, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

## Baseline Scenario 3

```{r}
shock_prod_model_shock=shock_prod_model %>% window(start= c(2006,3))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs3 <- list(

 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs3 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs3
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds

tilpas_pr_bs3 = Shock_bs3$simulation$tilpas_pr
u_ds_bs3 = Shock_bs3$simulation$u_ds
part_bs3 = Shock_bs3$simulation$part
nben_h_bs3 = Shock_bs3$simulation$nben_h
wage_ds_bs3 = Shock_bs3$simulation$wage_ds
dp_person_bs3 = Shock_bs3$simulation$dp_person
kont_h_ratio_bs3 = Shock_bs3$simulation$kont_h_ratio

nl_g_bs3 = Shock_bs3$simulation$nl_g
unemp_bs3 = Shock_bs3$simulation$unemp
s_h_bs3 = Shock_bs3$simulation$s_h
inflation_bs3 = Shock_bs3$simulation$inflation

yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod
prod_ds_bs3 = Shock_bs3$simulation$prod_ds
prod_ds_shock_bs3 = Shock_bs3$simulation$prod_ds_shock

ur_bs3 = Shock_bs3$simulation$ur
```

```{r}
plot(prod_bs3, col= "green"); lines(prod, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

## Baseline Scenario 4

```{r}
shock_kuld_model_shock=shock_kuld_model %>% window(start= c(2006,3))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs4 <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs4 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs4
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs4 = Shock_bs4$simulation$max_dp
wage_bs4 = Shock_bs4$simulation$wage
komp_r_bs4 = Shock_bs4$simulation$komp_r
part_bs4 = Shock_bs4$simulation$part
yk_ds_bs4 = Shock_bs4$simulation$yk_ds
pc_ds_bs4 = Shock_bs4$simulation$pc_ds
wage_ds_t_bs4 = Shock_bs4$simulation$wage_ds_t
ur_ds_bs4 = Shock_bs4$simulation$ur_ds
emp_bs4 = Shock_bs4$simulation$emp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds

tilpas_pr_bs4 = Shock_bs4$simulation$tilpas_pr
u_ds_bs4 = Shock_bs4$simulation$u_ds
part_bs4 = Shock_bs4$simulation$part
nben_h_bs4 = Shock_bs4$simulation$nben_h
wage_ds_bs4 = Shock_bs4$simulation$wage_ds
dp_person_bs4 = Shock_bs4$simulation$dp_person
kont_h_ratio_bs4 = Shock_bs4$simulation$kont_h_ratio

nl_g_bs4 = Shock_bs4$simulation$nl_g
unemp_bs4 = Shock_bs4$simulation$unemp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
wage_gap1_bs4 = Shock_bs4$simulation$wage_gap1
wage_gap_bs4 = Shock_bs4$simulation$wage_gap
prod_bs4 = Shock_bs4$simulation$prod
```

## Baseline Scenario 5

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs56 <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs56 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs56
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs56 = Shock_bs56$simulation$max_dp
wage_bs56 = Shock_bs56$simulation$wage
komp_r_bs56 = Shock_bs56$simulation$komp_r
part_bs56 = Shock_bs56$simulation$part
yk_ds_bs56 = Shock_bs56$simulation$yk_ds
pc_ds_bs56 = Shock_bs56$simulation$pc_ds
wage_ds_t_bs56 = Shock_bs56$simulation$wage_ds_t
ur_ds_bs56 = Shock_bs56$simulation$ur_ds
emp_bs56 = Shock_bs56$simulation$emp
yd_hk_ds_bs56 = Shock_bs56$simulation$yd_hk_ds

tilpas_pr_bs56 = Shock_bs56$simulation$tilpas_pr
u_ds_bs56 = Shock_bs56$simulation$u_ds
part_bs56 = Shock_bs56$simulation$part
nben_h_bs56 = Shock_bs56$simulation$nben_h
wage_ds_bs56 = Shock_bs56$simulation$wage_ds
dp_person_bs56 = Shock_bs56$simulation$dp_person
kont_h_ratio_bs56 = Shock_bs56$simulation$kont_h_ratio

nl_g_bs56 = Shock_bs56$simulation$nl_g
unemp_bs56 = Shock_bs56$simulation$unemp
yd_hk_ds_bs56 = Shock_bs56$simulation$yd_hk_ds
wage_gap1_bs56 = Shock_bs56$simulation$wage_gap1
wage_gap_bs56 = Shock_bs56$simulation$wage_gap
prod_bs56 = Shock_bs56$simulation$prod
```

## Baseline Scenario 5b Sens all

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs5b <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 sens_3 = TIMESERIES(sens_3+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs5b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs5b
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs5b = Shock_bs5b$simulation$max_dp
wage_bs5b = Shock_bs5b$simulation$wage
komp_r_bs5b = Shock_bs5b$simulation$komp_r
part_bs5b = Shock_bs5b$simulation$part
yk_ds_bs5b = Shock_bs5b$simulation$yk_ds
pc_ds_bs5b = Shock_bs5b$simulation$pc_ds
wage_ds_t_bs5b = Shock_bs5b$simulation$wage_ds_t
ur_ds_bs5b = Shock_bs5b$simulation$ur_ds
emp_bs5b = Shock_bs5b$simulation$emp
yd_hk_ds_bs5b = Shock_bs5b$simulation$yd_hk_ds

tilpas_pr_bs5b = Shock_bs5b$simulation$tilpas_pr
u_ds_bs5b = Shock_bs5b$simulation$u_ds
part_bs5b = Shock_bs5b$simulation$part
nben_h_bs5b = Shock_bs5b$simulation$nben_h
wage_ds_bs5b = Shock_bs5b$simulation$wage_ds
dp_person_bs5b = Shock_bs5b$simulation$dp_person
kont_h_ratio_bs5b = Shock_bs5b$simulation$kont_h_ratio

>>>>

```{r}
S_model$modelData <- within(S_model$modelData,{
  aa_check  = TSEXTEND(aa_check,  UPTO=c(2020,3))
})

S_model$modelData$aa_check
```

# Wage_ds Bs

@@

# Wage_ds Shock
